---
title: "Updated Fitness males"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r loading packages, echo = FALSE, include = FALSE}
# Function to check and install packages
install_if_needed <- function(pkg) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg)
  }
  library(pkg, character.only = TRUE)  # Load the package
}

# Check and install/load required libraries
install_if_needed("dplyr")
install_if_needed("tidyr")
install_if_needed("ggplot2")
install_if_needed("cowplot")
install_if_needed("sf")
install_if_needed("stringr")
install_if_needed("tidyverse")
install_if_needed("lme4")
install_if_needed("glmmTMB")
install_if_needed("janitor")
install_if_needed("ggeffects")
install_if_needed("lmerTest")
install_if_needed("emmeans")

```


```{r reading data, echo = FALSE, include = FALSE}
#using data for males before 2016
breeding_male <- read.csv("breeding_both_cutoff_final.csv") %>% 
  select(everything(), -X) 

lifetime_male <- read.csv("lifetime_both_final.csv") %>% 
  select(everything(), -X) %>% 
  filter(sex == "M")

```




### Breeding attempt traits -- effect of fathers' dispersal status

#### Lay date
```{r, echo = FALSE}
imm_laydate_male <- lmer(april_lay_date ~ disp_male + (1|study_year) + (1|box)  + (1|father), 
                        data = breeding_male)
summary(imm_laydate_male)

emmeans(imm_laydate_male, specs = "disp_male", type = "response")


```



#### Hatch date

```{r, echo = FALSE}
imm_hatchdate_male <- lmer(april_hatch_date ~ disp_male + (1|study_year) + (1|box) + (1|father), 
                          data = breeding_male)
summary(imm_hatchdate_male)

emmeans(imm_hatchdate_male, specs = "disp_male", type = "response")


```



#### Clutch size

```{r, echo = FALSE}
imm_clutchsize_male <- glmer(clutch_size ~ disp_male + (1|study_year) + (1|box) + (1|father), 
                           data = breeding_male,
                           family = "poisson")
summary(imm_clutchsize_male)

emmeans(imm_clutchsize_male, specs = "disp_male", type = "response")


```



#### Mean egg weight

```{r, echo = FALSE}
imm_eggweight_male <- lmer(mean_egg_weight ~ disp_male + (1|study_year) + (1|box) + (1|father), 
                          data = breeding_male)
summary(imm_eggweight_male)
## Warning: Model failed to converge with max|grad| = 0.0027882 (tol = 0.002, component 1)

emmeans(imm_eggweight_male, specs = "disp_male", type = "response")


plot(predict_response(imm_eggweight_male, terms = "disp_male"))



```



#### Proportion of eggs fledged

```{r, echo = FALSE}
imm_fledged_male <- glmer(prop_fledged ~ disp_male + (1|study_year) + (1|box) + (1|father), 
                         weights = clutch_size,
                         data = breeding_male,
                         family = binomial(link = "logit"))
summary(imm_fledged_male)

emmeans(imm_fledged_male, specs = "disp_male", type = "response")


```



#### Number of fledglings

```{r, echo = FALSE}
imm_fledglings_male <- glmmTMB(num_fledglings ~ disp_male + (1|study_year) + (1|box) + (1|father), 
                              data = breeding_male,
                              ziformula = ~.,
                              family = "poisson")
summary(imm_fledglings_male)

emmeans(imm_fledglings_male, specs = "disp_male", type = "response")


plot(predict_response(imm_fledglings_male, terms = "disp_male"))

```




#### Number of recruits

```{r, echo = FALSE}
imm_recruits_male <- glmer(num_recruits ~ disp_male + (1|study_year) + (1|box) + (1|father), 
                         data = filter(breeding_male, year < 2016),
                         family = poisson(link = "log"))
summary(imm_recruits_male)

emmeans(imm_recruits_male, specs = "disp_male", type = "response")

plot(predict_response(imm_recruits_male, terms = "disp_male"))

```



### Individual-level traits -- effect of fathers' dispersal status

#### Age of disappearance (reproductive lifespan)

```{r, echo = FALSE}
imm_age_male <- lmer(last_age ~ disp + (1|dob), 
                         data = lifetime_male)
summary(imm_age_male)

emmeans(imm_age_male, specs = "disp", type = "response")


plot(predict_response(imm_age_male, terms = "disp"))

```


#### Age of appearance (first breeding age)

```{r, echo = FALSE}
imm_firstage_male <- lmer(first_age ~ disp + (1|dob) , 
                         data = lifetime_male)
summary(imm_firstage_male)
### boundary (singular) fit: see help('isSingular')

emmeans(imm_firstage_male, specs = "disp", type = "response")

plot(predict_response(imm_firstage_male, terms = "disp"))

```

#### Number of breeding attempts

```{r, echo = FALSE}
imm_numattempts_male <- lmer(num_attempts ~ disp + (1|dob), 
                         data = lifetime_male)
summary(imm_numattempts_male)
### boundary (singular) fit: see help('isSingular')

emmeans(imm_numattempts_male, specs = "disp", type = "response")

```

#### Interval between first and last appearance

```{r, echo = FALSE}
imm_interval_male <- lmer(interval ~ disp + (1|dob), 
                         data = lifetime_male)
summary(imm_interval_male)

emmeans(imm_interval_male, specs = "disp", type = "response")

```


#### Lifetime number of recruits -- lifetime reproductive success

##### No fixed effect (only date of birth)

```{r}
imm_lrs_male <- glmer(lifetime_recruits ~ disp + (1|dob), 
                         data = lifetime_male,
                         family = poisson(link = "log"))
summary(imm_lrs_male)

emmeans(imm_lrs_male, specs = "disp", type = "response")


```

##### Number of attempts as fixed effect

```{r}
imm_lrs_male_numattempts <- glmer(lifetime_recruits ~ disp + (1|dob) + (1|num_attempts), 
                         data = lifetime_male,
                         family = poisson(link = "log"))
summary(imm_lrs_male_numattempts)

emmeans(imm_lrs_male_numattempts, specs = "disp", type = "response")


```


#### Lifetime number of fledglings -- lifetime reproductive success

```{r, echo = FALSE}
imm_lrsfledge_male <- glmmTMB(lifetime_fledglings ~ disp + (1|dob),
                              data = lifetime_male,
                              ziformula = ~.,
                              family = "poisson")
summary(imm_lrsfledge_male)

emmeans(imm_lrsfledge_male, specs = "disp", type = "response")


imm_lrsfledge_male_lastage <- glmmTMB(lifetime_fledglings ~ disp + (1|last_age) + (1|dob),
                              data = lifetime_male,
                              ziformula = ~.,
                              family = "poisson")
summary(imm_lrsfledge_male_lastage)

emmeans(imm_lrsfledge_male_lastage, specs = "disp", type = "response")


```



## Testing if effects dissipate over time

```{r adding attempt number to breeding_male}
breeding_time <- breeding_male %>% 
  group_by(mother) %>% 
  mutate(att_num_male = seq_along(mother)) %>% 
  ungroup() %>% 
  mutate(att_num_male = case_when(is.na(mother) == T ~ NA,
                                 is.na(mother) == F ~ att_num_male)) %>% 
  mutate(att_num_male_bin = case_when(att_num_male == 1 ~ att_num_male,
                                     att_num_male > 1 ~ 2)) %>% 
  mutate(att_num_male = as.factor(att_num_male),
         att_num_male_bin = as.factor(att_num_male_bin)) %>% 
    group_by(father) %>% 
  mutate(att_num_male = seq_along(father)) %>% 
  ungroup() %>% 
  mutate(att_num_male = case_when(is.na(father) == T ~ NA,
                                  is.na(father) == F ~ att_num_male)) %>% 
  mutate(att_num_male_bin = case_when(att_num_male == 1 ~ att_num_male,
                                     att_num_male > 1 ~ 2)) %>% 
  mutate(att_num_male = as.factor(att_num_male),
         att_num_male_bin = as.factor(att_num_male_bin))

filter(breeding_time, mother == "BA64007")


###NUMBERS ARE SLIGHTLY OFF, PLS FIX LATER

filter(breeding_time, is.na(att_num_male))

```




##### MALE: full attempt number

```{r, echo = FALSE}
imm_recruits_male_time <- glmer(num_recruits ~ disp_male+att_num_male + (1|study_year) + (1|box) + (1|father), 
                          data = filter(breeding_time, !att_num_male == 7),
                          family = poisson(link = "log"))
summary(imm_recruits_male_time)

emmeans(imm_recruits_male_time, specs = c("disp_male", "att_num_male"), type = "response")


plot(predict_response(imm_recruits_male_time, terms = c("disp_male", "att_num_male")))

```

##### MALE: binary

```{r, echo = FALSE}
imm_recruits_male_time_bin <- glmer(num_recruits ~ disp_male*att_num_male_bin + (1|study_year) + (1|box) + (1|father), 
                          data = filter(breeding_time, !att_num_male == 7),
                          family = poisson(link = "log"))
summary(imm_recruits_male_time_bin)

emmeans(imm_recruits_male_time_bin, specs = c("disp_male", "att_num_male_bin"), type = "response")


plot(predict_response(imm_recruits_male_time_bin, terms = c("disp_male", "att_num_male_bin")))


imm_recruits_male_time_bin2 <- glmer(num_recruits ~ disp_male+att_num_male_bin + (1|study_year) + (1|box) + (1|father), 
                          data = filter(breeding_time, !att_num_male == 7),
                          family = poisson(link = "log"))
summary(imm_recruits_male_time_bin2)
pairs(
  emmeans(imm_recruits_male_time_bin2, specs = c("disp_male", "att_num_male_bin")),
  adjust = "tukey"
)
  emmeans(imm_recruits_male_time_bin2, specs = c("disp_male", "att_num_male_bin"), type = "response")


```

