---
title: "Updated Fitness Females"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r loading packages, echo = FALSE, include = FALSE}
# Function to check and install packages
install_if_needed <- function(pkg) {
  if (!requireNamespace(pkg, quietly = TRUE)) {
    install.packages(pkg)
  }
  library(pkg, character.only = TRUE)  # Load the package
}

# Check and install/load required libraries
install_if_needed("dplyr")
install_if_needed("tidyr")
install_if_needed("ggplot2")
install_if_needed("cowplot")
install_if_needed("sf")
install_if_needed("stringr")
install_if_needed("tidyverse")
install_if_needed("lme4")
install_if_needed("glmmTMB")
install_if_needed("janitor")
install_if_needed("ggeffects")
install_if_needed("lmerTest")
install_if_needed("emmeans")

```


```{r reading data, echo = FALSE, include = FALSE}
#using data for females before 2016
breeding_fem <- read.csv("breeding_both_cutoff_final.csv") %>% 
  select(everything(), -X) 

lifetime_fem <- read.csv("lifetime_both_final.csv") %>% 
  select(everything(), -X) %>% 
  filter(sex == "F")

breeding_fem
mean(breeding_fem$num_fledglings)
sd(breeding_fem$num_fledglings)

test <- lifetime_fem %>% 
  group_by(year) %>% 
  summarise(disp)

test_counts <- data.frame(year = unique(test$year),
                          prop = c(0))
x <- 2015

test_counts <- dplyr::count(test, disp) %>% 
  pivot_wider(names_from = disp, values_from = n)
colnames(test_counts) <- c("year", "dispersing", "locally_born")
test_counts <- test_counts %>% 
  mutate(count = dispersing + locally_born) %>% 
  mutate(prop = dispersing/count)

sum(test_counts$count, na.rm=T)
summary(test_counts$prop)
sd(test_counts$prop, na.rm=T)

lifetime <- read.csv("lifetime_both_final.csv") %>% 
  select(everything(), -X) 

table(lifetime$disp)
test2 <- lifetime %>% 
  group_by(year) %>% 
  summarise(disp)
test_counts2 <- dplyr::count(test2, disp) %>% 
  pivot_wider(names_from = disp, values_from = n)
colnames(test_counts2) <- c("year", "dispersing", "locally_born")
test_counts2 <- test_counts2 %>% 
  mutate(count = dispersing + locally_born) %>% 
  mutate(prop = dispersing/count)
sum(test_counts2$count, na.rm=TRUE)
summary(test_counts2$prop)

```




### Breeding attempt traits -- effect of mothers' dispersal status

#### Lay date
```{r, echo = FALSE}
imm_laydate_fem <- lmer(april_lay_date ~ disp_fem + (1|study_year) + (1|box)  + (1|mother), 
                        data = breeding_fem)
summary(imm_laydate_fem)

emmeans(imm_laydate_fem, specs = "disp_fem", type = "response")


```



#### Hatch date

```{r, echo = FALSE}
imm_hatchdate_fem <- lmer(april_hatch_date ~ disp_fem + (1|study_year) + (1|box) + (1|mother), 
                          data = breeding_fem)
summary(imm_hatchdate_fem)

emmeans(imm_hatchdate_fem, specs = "disp_fem", type = "response")


```



#### Clutch size

```{r, echo = FALSE}
imm_clutchsize_fem <- glmer(clutch_size ~ disp_fem + (1|study_year) + (1|box) + (1|mother), 
                           data = breeding_fem, 
                           family = "poisson")
summary(imm_clutchsize_fem)

emmeans(imm_clutchsize_fem, specs = "disp_fem", type = "response")


```



#### Mean egg weight

```{r, echo = FALSE}
imm_eggweight_fem <- lmer(mean_egg_weight ~ disp_fem + (1|study_year) + (1|box) + (1|mother), 
                          data = breeding_fem)
summary(imm_eggweight_fem)
## Warning: Model failed to converge with max|grad| = 0.0027882 (tol = 0.002, component 1)

emmeans(imm_eggweight_fem, specs = "disp_fem", type = "response")


plot(predict_response(imm_eggweight_fem, terms = "disp_fem"))



```



#### Proportion of eggs fledged

```{r, echo = FALSE}
imm_fledged_fem <- glmer(prop_fledged ~ disp_fem + (1|study_year) + (1|box) + (1|mother), 
                         weights = clutch_size,
                         data = breeding_fem,
                         family = binomial(link = "logit"))
summary(imm_fledged_fem)

emmeans(imm_fledged_fem, specs = "disp_fem", type = "response")


plot(predict_response(imm_fledged_fem, terms = c("disp_fem")))

```



#### Number of fledglings

```{r, echo = FALSE}
imm_fledglings_fem <- glmmTMB(num_fledglings ~ disp_fem + (1|study_year) + (1|box) + (1|mother), 
                              data = breeding_fem,
                              ziformula = ~.,
                              family = "poisson")
summary(imm_fledglings_fem)

emmeans(imm_fledglings_fem, specs = "disp_fem", type = "response")


plot(predict_response(imm_fledglings_fem, terms = "disp_fem"))

```




#### Number of recruits

```{r, echo = FALSE}
imm_recruits_fem <- glmer(num_recruits ~ disp_fem + (1|study_year) + (1|box) + (1|mother), 
                         data = filter(breeding_fem, year < 2016),
                         family = poisson(link = "log"))
summary(imm_recruits_fem)

emmeans(imm_recruits_fem, specs = "disp_fem", type = "response")


plot(predict_response(imm_recruits_fem, terms = "disp_fem"))

```



### Individual-level traits -- effect of mothers' dispersal status

#### Age of disappearance (reproductive lifespan)

```{r, echo = FALSE}
imm_age_fem <- lmer(last_age ~ disp + (1|dob), 
                         data = lifetime_fem)
summary(imm_age_fem)

emmeans(imm_age_fem, specs = "disp", type = "response")


plot(predict_response(imm_age_fem, terms = "disp"))

table(breeding_fem$disp_fem, breeding_fem$fem_breed_age) 
table(breeding_fem$disp_male, breeding_fem$male_breed_age)

```


#### Age of appearance (first breeding age)

```{r, echo = FALSE}
imm_firstage_fem <- lmer(first_age ~ disp + (1|dob) , 
                         data = lifetime_fem)
summary(imm_firstage_fem)
### boundary (singular) fit: see help('isSingular')

emmeans(imm_firstage_fem, specs = "disp", type = "response")


plot(predict_response(imm_firstage_fem, terms = "disp"))

```

#### Number of breeding attempts

```{r, echo = FALSE}
imm_numattempts_fem <- lmer(num_attempts ~ disp + (1|dob), 
                         data = lifetime_fem)
summary(imm_numattempts_fem)

emmeans(imm_numattempts_fem, specs = "disp", type = "response")


plot(predict_response(imm_numattempts_fem, temrs = "disp"))

### boundary (singular) fit: see help('isSingular')

```

#### Interval between first and last appearance

```{r, echo = FALSE}
imm_interval_fem <- lmer(interval ~ disp + (1|dob), 
                         data = lifetime_fem)
summary(imm_interval_fem)

emmeans(imm_interval_fem, specs = "disp", type = "response")


```


#### Lifetime number of recruits -- lifetime reproductive success

##### No fixed effect (only date of birth)

```{r}
imm_lrs_fem <- glmer(lifetime_recruits ~ disp + (1|dob), 
                         data = lifetime_fem,
                         family = poisson(link = "log"))
summary(imm_lrs_fem)

emmeans(imm_lrs_fem, specs = "disp", type = "response")

```

##### Number of attempts as fixed effect

```{r}
imm_lrs_fem_numattempts <- glmer(lifetime_recruits ~ disp + (1|dob) + (1|num_attempts), 
                         data = lifetime_fem,
                         family = poisson(link = "log"))
summary(imm_lrs_fem_numattempts)

emmeans(imm_lrs_fem_numattempts, specs = "disp", type = "response")


```


#### Lifetime number of fledglings -- lifetime reproductive success

```{r, echo = FALSE}
imm_lrsfledge_fem <- glmmTMB(lifetime_fledglings ~ disp + (1|dob),
                              data = lifetime_fem,
                              ziformula = ~.,
                              family = "poisson")
summary(imm_lrsfledge_fem)

emmeans(imm_lrsfledge_fem, specs = "disp", type = "response")


imm_lrsfledge_fem_lastage <- glmmTMB(lifetime_fledglings ~ disp + (1|last_age) + (1|dob),
                              data = lifetime_fem,
                              ziformula = ~.,
                              family = "poisson")
summary(imm_lrsfledge_fem_lastage)

emmeans(imm_lrsfledge_fem_lastage, specs = "disp", type = "response")


```



## Testing if effects dissipate over time

```{r adding attempt number to breeding_fem}
breeding_time <- breeding_fem %>% 
  group_by(mother) %>% 
  mutate(att_num_fem = seq_along(mother)) %>% 
  ungroup() %>% 
  mutate(att_num_fem = case_when(is.na(mother) == T ~ NA,
                                 is.na(mother) == F ~ att_num_fem)) %>% 
  mutate(att_num_fem_bin = case_when(att_num_fem == 1 ~ att_num_fem,
                                     att_num_fem > 1 ~ 2)) %>% 
  mutate(att_num_fem = as.factor(att_num_fem),
         att_num_fem_bin = as.factor(att_num_fem_bin)) %>% 
    group_by(father) %>% 
  mutate(att_num_male = seq_along(father)) %>% 
  ungroup() %>% 
  mutate(att_num_male = case_when(is.na(father) == T ~ NA,
                                  is.na(father) == F ~ att_num_male)) %>% 
  mutate(att_num_male_bin = case_when(att_num_male == 1 ~ att_num_male,
                                     att_num_male > 1 ~ 2)) %>% 
  mutate(att_num_male = as.factor(att_num_male),
         att_num_male_bin = as.factor(att_num_male_bin))

filter(breeding_time, mother == "BA64007")


###NUMBERS ARE SLIGHTLY OFF, PLS FIX LATER

filter(breeding_time, is.na(att_num_male))

```


##### Using normal model structure

```{r, echo = FALSE}
imm_recruits_fem_time <- glmer(num_recruits ~ disp_fem*att_num_fem + (1|study_year) + (1|box) + (1|mother), 
                         data = filter(breeding_time, !att_num_fem == 7),
                         family = poisson(link = "log"))
summary(imm_recruits_fem_time)

emmeans(imm_recruits_fem_time, specs = c("disp_fem", "att_num_fem"), type = "response")

pairs(
  emmeans(imm_recruits_fem_time, specs = c("disp_fem", "att_num_fem")),
  adjust = "tukey"
)


plot(predict_response(imm_recruits_fem_time, terms = c("disp_fem", "att_num_fem")))


```

##### FEMALE: binary

```{r, echo = FALSE}
imm_recruits_fem_time_bin <- glmer(num_recruits ~ disp_fem*att_num_fem_bin + (1|study_year) + (1|box) + (1|mother), 
                         data = filter(breeding_time, is.na(mother) == F),
                         family = poisson)
summary(imm_recruits_fem_time_bin)

emmeans(imm_recruits_fem_time_bin, specs = c("disp_fem", "att_num_fem_bin"), type = "response")

pairs(
  emmeans(imm_recruits_fem_time_bin, specs = c("disp_fem", "att_num_fem_bin")),
  adjust = "tukey"
)


plot(predict_response(imm_recruits_fem_time_bin, terms = c("disp_fem", "att_num_fem_bin")))


imm_recruits_fem_time_bin2 <- glmer(num_recruits ~ disp_fem+att_num_fem_bin + (1|study_year) + (1|box) + (1|mother), 
                         data = filter(breeding_time, is.na(mother) == F),
                         family = poisson)
summary(imm_recruits_fem_time_bin2)
pairs(
  emmeans(imm_recruits_fem_time_bin2, specs = c("disp_fem", "att_num_fem_bin")),
  adjust = "tukey"
)
  emmeans(imm_recruits_fem_time_bin2, specs = c("disp_fem", "att_num_fem_bin"), type = "response")

```



